---
title: "Regression Assignment 2"
author: "Kristin Gmunder"
date: "11/16/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 2. Calculate Multiple Regression Estimates
Now consider the multiple linear regression model. Modify your function from last class to take in a numeric response vector `y` and a numeric design matrix `X`. This function should return a *named* vector of the regression coefficients from the linear model
\[
\hat{\textbf{y}} = \beta_0 + \beta_1\textbf{x}_1 + \beta_2\textbf{x}_2 + \ldots + \beta_p\textbf{x}_p.
\]
Your function should use the formula you derived in Part 1 to calculate these estimates directly (that is, without a call to the `lm()` or any other modelling function in R).

A few details:

1. If the data matrix `X` has column names, the names for the vector of regression coefficients should be `"Intercept"` plus those names. Otherwise, the names should be `"Intercept"`, `"beta1"`, `"beta2"`, ..., `"betap"` (where `p` is the number of predictors in `X`). See the `paste0()` help documentation. 
2. Remember that the design matrix `X` probably doesn't have the leading column of 1s that we need to estimate $\beta_0$.
3. Matrix multiplication uses different functions in R. See the help files for `t()`, `%*%`, and `solve()`.
4. Matrix math in R is different between matrices and data frames (*why?*). Make sure to account for both of these input options.

Use your function to calculate the regression coefficients for
\[
\text{chol}_i = \beta_0 + \beta_1\text{age}_i + \beta_2\text{weight}_i + \beta_3\text{sbp}_i + \varepsilon_i,\quad i = 1, \ldots, n
\]
from the WCGS data. Compare the intercept and coefficients you calculated to those returned by the `lm()` function. I get this output:
```{r echo = FALSE}
#  Set-up and Making the Design Matrix
wcgs_df <- read.csv(file = "/Users/KristinGmunder/Documents/wcgs.csv", header = TRUE, stringsAsFactors = FALSE)
lm(chol ~ age + weight + sbp, data = wcgs_df)
age <- matrix(wcgs_df$age)
weight <- matrix(wcgs_df$weight)
sbp <- matrix(wcgs_df$sbp)
chol <- matrix(wcgs_df$chol)

library(tidyverse)
wcgs_mat <-
# Take the wcgs data frame
wcgs_df %>% 
# select the output and three predictor columns
select(chol, age, weight, sbp) %>% 
# remove the subjects with missing values (12 rows)
na.omit() %>% 
# and turn it into a matrix
as.matrix()

head(wcgs_mat)

X <- wcgs_mat[, c("age", "weight", "sbp")]
head(X)

Y <- wcgs_mat[, c("chol")]

```



```{r}
# Function
findTheBetas <- function(X, Y) {
  X <- as.matrix(X) 
  Y <- as.matrix(Y) 
  check <- na.omit(cbind(Y, X))
  X <- as.matrix(check[ , -1])
  Y <- as.matrix(check[ , 1])
  interceptCol <- matrix(1, nrow = nrow(X))
  X <- cbind(interceptCol, X)
  XT <- t(X)
  XTX <- XT %*% X
  inv_XTX <- solve(XTX)
  estBeta <- inv_XTX %*% XT %*% Y
  if (is.null(colnames(X))) {
    rownames(estBeta) <- c("intercept", paste0("beta", 1:(ncol(X) - 1)))
  } else {
    rownames(estBeta)[1] <- "intercept"
  }
estBeta
}  

findTheBetas(X, Y)
```

