---
title: "RegressionNotes3"
author: "Kristin Gmunder"
date: "11/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
wcgs_df <- read.csv(file = "/Users/KristinGmunder/Documents/wcgs.csv", header = TRUE, stringsAsFactors = FALSE)
chol_mod <- lm(chol ~ age + weight + sbp, data = wcgs_df)
```

### Assumption 1: Model Errors are Normally Distributed
Overall, the residuals appear to be normally distributed, based on the histogram, but we may have a few outliers.
```{r}
str(chol_mod)
# Histogram
hist(chol_mod$residuals)

# QQ-Plot
qqnorm(chol_mod$residuals)
qqline(chol_mod$residuals)
```

Try a transformation
```{r}
hist(chol_mod$residuals)
cholSq_mod <- lm(sqrt(chol) ~ age + weight + sbp, data = wcgs_df)
hist(cholSq_mod$residuals)
qqnorm(cholSq_mod$residuals)
qqline(cholSq_mod$residuals)

```
That's probably worse. Let's leave the data alone...

### Assumption 2: Model Errors are Centered at 0
The quick and dirty way would be to look at the center of the histogram.  We can also perform a statistical test:
```{r}
t.test(chol_mod$residuals, mu = 0)
```
O is dead-set in the middle of the CI.  We're rather cocnfident that the meant of the residuals is close enough to 0.

### Assumption 3: Model Errors are Homoskedastic

